TODO

### 2024-12-13 write-ups/kid_tangrams_cogsci_2025/kid_tangrams_cogsci_2025.Rmd
save model summaries

expt_1 <- "data/expt_1"
expt_2 <- "data/expt_2"
mod_loc <- "code/models"
time_palette <- c("practice" = "grey", "block 1" = "#E41A1C", "block 2" = "#377EB8", "block 3" = "#4DAF4A", "block 4" = "purple") # TODO FIX

@@

>>>>

expt_1 <- "data/expt_1"
expt_2 <- "data/expt_2"
mod_loc <- "code/models"
mod_results <- "code/models/summary"
mod_form <- "code/models/formulae"
time_palette <- c("practice" = "grey", "block 1" = "#E41A1C", "block 2" = "#377EB8", "block 3" = "#4DAF4A", "block 4" = "purple") # TODO FIX

@@

library(tidybayes)

save_summary <- function(model) {
  intervals <- gather_draws(model, `b_.*`, regex = T) %>% mean_qi()

  stats <- gather_draws(model, `b_.*`, regex = T) %>%
    mutate(above_0 = ifelse(.value > 0, 1, 0)) %>%
    group_by(.variable) %>%
    summarize(pct_above_0 = mean(above_0)) %>%
    left_join(intervals, by = ".variable") %>%
    mutate(
      lower = .lower,
      upper = .upper,
      Term = str_sub(.variable, 3, -1),
      Estimate = .value
    ) %>%
    select(Term, Estimate, lower, upper)

  stats
}

form <- function(model) {
  dep <- as.character(model$formula[2])
  ind <- as.character(model$formula[3])

  str_c(dep, " ~ ", ind) %>%
    str_replace_all(" ", "") %>%
    str_replace_all("\\*", " $\\\\times$ ") %>%
    str_replace_all("\\+", "&nbsp;+ ") %>%
    str_replace_all("~", "$\\\\sim$ ")
}

do_model <- function(path) {
  model <- read_rds(here(mod_loc, path))
  save_summary(model) |> write_rds(here(mod_loc, "summary", path))
  model$formula |> write_rds(here(mod_loc, "formulae", path))
  print(summary(model))
}

mods <- list.files(path = here(mod_loc), pattern = ".*rds") |> walk(~ do_model(.))
